Finding Optimal Sequences for Area Aggregation --\protect\\ \Astar vs. Integer Linear Programming

### 2018-07-24 area_agg_seq_tsas.tex
working on including packages

\documentclass[acmlarge,review,natbib=false]{acmart}

%%drt24 hacks
%% Letter paper
%\setlength{\paperheight}{11in}
%\setlength{\paperwidth}{8.5in}

% Hack to try to make acmart work with biblatex: https://tex.stackexchange.com/questions/37076/is-it-possible-to-load-biblatex-with-a-class-that-has-already-loaded-natbib

\let\citename\relax
\RequirePackage[abbreviate=true, dateabbrev=true, isbn=true, doi=true, urldate=comp, url=true, maxbibnames=9, backref=false, backend=bibtex, style=ACM-Reference-Format, language=american,natbib]{biblatex}

%\usepackage{textcomp}
%\renewcommand{\textuparrow}{$\uparrow$}

%\addbibresource{sample-bibliography-biblatex.bib}
\addbibresource{Reference/BibReference.bib}

\renewcommand{\bibfont}{\Small}

\usepackage{booktabs} % For formal tables
\input{area_agg_seq_tsas_setting}

%% Copyright
%%\setcopyright{none}
%%\setcopyright{acmcopyright}
%%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%%\setcopyright{usgov}
%%\setcopyright{usgovmixed}
%%\setcopyright{cagov}
%%\setcopyright{cagovmixed}
%
%
%% DOI
%\acmDOI{10.475/123_4}
%
%% ISBN
%\acmISBN{123-4567-24-567/08/06}
%
%%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA}
%\acmYear{1997}
%\copyrightyear{2016}
%
%\acmPrice{15.00}

\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmJournal{PACMHCI}
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2010}
\acmMonth{3}
\acmArticleSeq{11}

%\acmBadgeR[http://ctuning.org/ae/ppopp2016.html]{ae-logo}
%\acmBadgeL[http://ctuning.org/ae/ppopp2016.html]{ae-logo}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{0000001.0000001}

% Paper history
\received{February 2007}
\received{March 2009}
\received[accepted]{June 2009}

@@

%% The default list of authors is too long for headers}
%\renewcommand{\shortauthors}{B. Trovato et al.}

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{ACM proceedings, \LaTeX, text tagging}
\keywords{Continuous map generalization, Land cover, 
	 Type chang, Compactness, Graph, Optimization, Exponential}

@@

Now we need to make sure that
patch~$o$ with $w_{t,o}=1$ is indeed 
a smallest patch at time~$t$.
We define variable~$A_{t,r}$ as the area of 
patch~$r$ at time~$t$, 
that is,
\begin{flalign*}
&\eqquad
\embrd[S]{A_{t,r}} = 
\embld[T]{\sum_{p\in P} a_p \cdot x_{t,p,r},} &
\end{flalign*}
where~$a_p$ is the area of polygon~$p$ 
and is a constant (as viewed by the ILP).
Area~$A_{t,r}$ is positive 
if and only if polygon~$r$ is a center at time~$t$,
that is, if and only if~$x_{t,r,r}=1$.
We define a very large number~$M$ 
to help us construct the corresponding constraints.
It suffices to set~$M$ to 
the area of the whole region, 
i.e., $M=A_R$ (see \eq\ref{eq:f_type}). 
We require that
%\begin{flalign}
%\label{eq:CstrSIndeedSmallest}
%&\eqquad
%\embrd[S]{A_{t,o} - M(1-w_{t,o})} \le
%\embld[T]{A_{t,r}+M(1-x_{t,r,r})} \inquad
%\forall t 	 \in {T}\setminus \{n\}, 
%\forall o, r \in P \text{~with}~o\ne r. &
%\end{flalign}
%\begin{flalign}
%\label{eq:CstrSIndeedSmallest}
%&\eqquad
%\embrd[S]{A_{t,o}} -
%\embld[T]{M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r})} \inquad
%\forall t 	 \in {T}\setminus \{n\}, 
%\forall o, r \in P \text{~with}~o\ne r. &
%\end{flalign}
\begin{equation}
A_{t,o} - M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r}) \inquad
\forall t 	 \in {T}\setminus \{n\}, 
\forall o, r \in P \text{~with}~o\ne r.
\end{equation}
This constraint takes effect only when~$w_{t,o}=1$ 
and~$x_{t,r,r}=1$, which indicates that 
patch~$o$ is smaller than or equal to 
all the other existing patches at time~$t$.

>>>>

\documentclass[acmlarge,review,natbib=false]{acmart}
\input{area_agg_seq_tsas_setting}

@@

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10010405.10010476.10010479</concept_id>
	<concept_desc>Applied computing~Cartography</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Applied computing~Cartography}

\keywords{Continuous map generalization, Land cover, 
	 Type chang, Compactness, Graph, Optimization, Exponential}

@@

Now we need to make sure that
patch~$o$ with $w_{t,o}=1$ is indeed 
a smallest patch at time~$t$.
We define variable~$A_{t,r}$ as the area of 
patch~$r$ at time~$t$, 
that is,
\begin{flalign*}
&\eqquad
\embrd[S]{A_{t,r}} = 
\embld[T]{\sum_{p\in P} a_p \cdot x_{t,p,r},} &
\end{flalign*}
where~$a_p$ is the area of polygon~$p$ 
and is a constant (as viewed by the ILP).
Area~$A_{t,r}$ is positive 
if and only if polygon~$r$ is a center at time~$t$,
that is, if and only if~$x_{t,r,r}=1$.
We define a very large number~$M$ 
to help us construct the corresponding constraints.
It suffices to set~$M$ to 
the area of the whole region, 
i.e., $M=A_R$ (see \eq\ref{eq:f_type}). 
We require that
%\begin{flalign}
%\label{eq:CstrSIndeedSmallest}
%&\eqquad
%\embrd[S]{A_{t,o} - M(1-w_{t,o})} \le
%\embld[T]{A_{t,r}+M(1-x_{t,r,r})} \inquad
%\forall t 	 \in {T}\setminus \{n\}, 
%\forall o, r \in P \text{~with}~o\ne r. &
%\end{flalign}
\begin{flalign}
\label{eq:CstrSIndeedSmallest}
&\eqquad
\embrd[S]{A_{t,o}} -
\embld[T]{M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r})} \inquad
\forall t 	 \in {T}\setminus \{n\}, 
\forall o, r \in P \text{~with}~o\ne r. &
\end{flalign}
%\begin{equation}
%A_{t,o} - M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r}) \inquad
%\forall t 	 \in {T}\setminus \{n\}, 
%\forall o, r \in P \text{~with}~o\ne r.
%\end{equation}
This constraint takes effect only when~$w_{t,o}=1$ 
and~$x_{t,r,r}=1$, which indicates that 
patch~$o$ is smaller than or equal to 
all the other existing patches at time~$t$.
